---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

Read csv, put into data.frame.
```{r, echo=TRUE}
activity = read.csv('activity.csv')
df = data.frame(activity)
```

## What is mean total number of steps taken per day?

```{r, echo=TRUE}
library(dplyr)
df_steps <- data.frame(df %>% 
  group_by(date) %>% 
  summarise(count = sum(steps),
            mean = mean(steps, na.rm=TRUE),
            median = median(steps, na.rm=TRUE)))
rownames(df_steps) = df_steps$date
df_steps$date = NULL
df_steps[,'count', drop=FALSE]
```

## What is the average daily activity pattern?

Histogram of steps taken per day:
```{r, echo=TRUE}
hist(df_steps$count)
```
Mean and median of steps per day:
```{r, echo=TRUE}
df_steps[, 'mean', drop=FALSE]
df_steps[,'median', drop=FALSE]
```
Plot average steps for each 5-minute interval:
```{r, echo=TRUE}
df_intervals = data.frame(df %>% 
  group_by(interval) %>% 
  summarise(mean = mean(steps, na.rm=TRUE)))
df$date = as.Date(df$date)
plot(df_intervals$interval, y = df_intervals$mean, plot.type = 'l')
apply(df_intervals, MARGIN = 2, function(x) max(x, na.rm=TRUE))
```

## Imputing missing values
Number of missing values
```{r, echo=TRUE}
sum(is.na(df$steps))
```
Impute mean of each 5-minute interval:
```{r, echo=TRUE}
df_copy = cbind(df)
for (i in unique(df_copy$interval))
    df_copy[df_copy$interval==i & is.na(df_copy$steps),'steps']=df_intervals[df_intervals$interval==i,'mean']
df_copy_steps <- data.frame(df_copy %>% 
  group_by(date) %>% 
  summarise(count = sum(steps),
            mean = mean(steps, na.rm=TRUE),
            median = median(steps, na.rm=TRUE)))
```
```{r}
hist(df_copy_steps$count)
```

## Are there differences in activity patterns between weekdays and weekends?

Make weekdays variable:

```{r, echo=TRUE}
df_copy$weekday = weekdays(df_copy$date)
df_copy$day_type = ifelse(df_copy$weekday=='Saturday' | df_copy$weekday=='Sunday', 'Weekend', 'Weekday')

df_copy_intervals = data.frame(df_copy %>% 
  group_by(interval, day_type) %>% 
  summarise(mean = mean(steps, na.rm=TRUE)))
```
Plot:
```{r, echo=TRUE}
library('ggplot2')
ggplot(data=df_copy_intervals, aes(x=interval, y=mean))+geom_line()+facet_wrap(~day_type, nrow=2)
```
